### 2017-10-09 mcmc.tex
start reformatting for arXiv and ApJ

% This file is part of the MCMC project,
%   which is (in turn) part of the Data Analysis Recipes project.
% Copyright 2013, 2014, 2015, 2016 David W. Hogg (NYU) and Dan Foreman-Mackey (NYU, UW).

@@

% low priority
% ------------
% - Make endnote numbers clickable links to endnotes and back.  Relevant ideas here:
%   http://tex.stackexchange.com/questions/8452/making-endnotes-clickable-links-with-hyperref

@@

\documentclass[12pt,twoside,pdftex]{article}
\usepackage{styles/dar_endnotes}

@@

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing\thispagestyle{plain}%
%
\section*{Data analysis recipes:\\ \chaptertitle\footnotemark}
%
\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2013, 2014, 2015, 2016 the authors (OMG this took us a long time).
        This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Will Farr (Birmingham),
          Jonathan Goodman (NYU),
          Fengji Hou (NYU),
          Dustin Lang (CMU),
          Phil Marshall (KIPAC), and
          Iain Murray (Edinburgh)
        for valuable advice and comments over the years, and
          Alessandro Gentilini
        for a very close read.
        This project benefitted from various research grants, especially
          NSF grants AST-0908357, IIS-1124794, and AST-1517237,
          NASA grant NNX12AI50G,
          and the The Moore-Sloan Data Science Environment at NYU.}
}

\noindent
\textbf{David~W.~Hogg}\\
\affil{Simons~Center~for~Data~Analysis,
       Simons~Foundation}\\
\affil{Center~for~Cosmology~and~Particle~Physics, Department~of~Physics,
       New~York~University}\\
\affil{Center~for~Data~Science,
       New~York~University}\\
\affil{Max-Planck-Institut~f\"ur~Astronomie, Heidelberg}\\[1ex]
\textbf{Daniel~Foreman-Mackey}\\
\affil{Sagan Fellow}\\
\affil{Department~of~Astronomy, University~of~Washington}

@@

The first couple of \sectionname s will describe what a sampling is, and how
the simplest \MCMC\ method, the Metropolis-Hastings algorithm, can
provide one.
The next few \sectionname s will provide ideas about how to
initialize, tune and operate \MCMC\ methods for good performance.
The last few \sectionname s will provide advice for making decisions
among the myriad \MCMC\ methods implementations, how to implement a good
likelihood function and prior pdf function for inference, and how to
trouble-shoot standard kinds of problems that arise in operating \MCMC\
methods on real problems.
We will leave parenthetical and philosophical matters to the end-notes,
which appear after the main text.

@@

\clearpage
\markright{Notes}\theendnotes

\clearpage

>>>>

% This file is part of the MCMC project,
%   which is (in turn) part of the Data Analysis Recipes project.
% Copyright 2013, 2014, 2015, 2016, 2017 David W. Hogg (NYU) and Dan Foreman-Mackey (NYU, UW).

@@

@@

\documentclass[12pt,pdftex]{article}

@@

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing\thispagestyle{plain}%
%
\section*{Data analysis recipes:\\ \chaptertitle\note{%
\label{note:first}%
Copyright 2013, 2014, 2015, 2016, 2017 the authors (OMG this took us a long time).
        This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}}%
\noindent
\textbf{David~W.~Hogg}\\
\affil{Flatiron Institute, a division of the Simons~Foundation}\\
\affil{Center~for~Cosmology~and~Particle~Physics, Department~of~Physics,
       New~York~University}\\
\affil{Center~for~Data~Science,
       New~York~University}\\
\affil{Max-Planck-Institut~f\"ur~Astronomie, Heidelberg}\\[1ex]
\textbf{Daniel~Foreman-Mackey}\\
\affil{Flatiron Institute, a division of the Simons~Foundation}\\
\affil{Department~of~Astronomy, University~of~Washington}

@@

The first couple of \sectionname s will describe what a sampling is, and how
the simplest \MCMC\ method, the Metropolis-Hastings algorithm, can
provide one.
The next few \sectionname s will provide ideas about how to
initialize, tune and operate \MCMC\ methods for good performance.
The last few \sectionname s will provide advice for making decisions
among the myriad \MCMC\ methods implementations, how to implement a good
likelihood function and prior pdf function for inference, and how to
trouble-shoot standard kinds of problems that arise in operating \MCMC\
methods on real problems.
We will leave parenthetical and philosophical matters to the footnotes,
which appear after the main text.

@@

\clearpage
\paragraph{Acknowledgements:}
We would like to thank
          Alex Barnett (Flatiron),
          Jo Bovy (Toronto),
          Brendon Brewer (Auckland),
          Will Farr (Flatiron)
          Jonathan Goodman (NYU),
          Fengji Hou (NYU),
          Dustin Lang (Toronto),
          Phil Marshall (KIPAC), and
          Iain Murray (Edinburgh)
        for valuable advice and comments over the years, and
          Alessandro Gentilini
        for a very close read.
        This project benefitted from various research grants, especially
          NSF grants AST-0908357, IIS-1124794, and AST-1517237,
          NASA grant NNX12AI50G,
          and the The Moore-Sloan Data Science Environment at NYU.
